FitBit Analysis

### 2023-02-14 01_studies/01_Laborstudie ProVisioNET/R script/demographic data/demographic data.Rmd

# rename columns
demo.data <- rename(demo.data, c("Group" = "LI06_05",
                                  "Gender" = "LI02_01_1",
                                  "Age" = "LI03_01",
                                  "Teaching Experience" = "LI04_01")) %>% 
    filter(Group %in% c(101:125, 202:217))# filter relevant rows

>>>>

# rename columns
demo.data <- rename(demo.data, c("Group" = "LI06_05",
                                  "Gender" = "LI02_01_1",
                                  "Age" = "LI03_01",
                                  "Teaching Experience" = "LI04_01")) %>% 
    filter(Group %in% c(101:136, 202:217))# filter relevant rows

### 2023-02-14 02_paper/02_study/02_fitbit paper/fitbit_paper.Rmd

# Mean, SD and range for disruption and confident factor
rating_table <- 
  df_rating %>% 
  filter(!is.na(confident_factor),
         !is.na(disruption_factor)) %>% 
   summarise("M disruption factor" = round(mean(disruption_factor),
                                     digits = 2),
            "SD disruption factor" = round(sd(disruption_factor),
                                      digits = 2),
            "Min disruption factor" = min(disruption_factor),
            "Max disruption factor" = max(disruption_factor),
            "M confident factor" = round(mean(confident_factor),
                                     digits = 2),
            "SD confident factor" = round(sd(confident_factor),
                                      digits = 2),
            "Min confident factor" = min(confident_factor),
            "Max confident factor" = max(confident_factor)
            )

>>>>

# Mean, SD and range for disruption and confidence factor
rating_table <- 
  df_rating %>% 
  filter(!is.na(confidence_factor),
         !is.na(disruption_factor)) %>% 
   summarise("M disruption factor" = round(mean(disruption_factor),
                                     digits = 2),
            "SD disruption factor" = round(sd(disruption_factor),
                                      digits = 2),
            "Min disruption factor" = min(disruption_factor),
            "Max disruption factor" = max(disruption_factor),
            "M confidence factor" = round(mean(confidence_factor),
                                     digits = 2),
            "SD confidence factor" = round(sd(confidence_factor),
                                      digits = 2),
            "Min confidence factor" = min(confidence_factor),
            "Max confidence factor" = max(confidence_factor)
            )
